---
title: "Bayes net manipulation with Peanut :: Cheat Sheet"
description: " "
execute:
  eval: true
  output: false
  warning: false
---

```{r}
#| output: asis
#| echo: false
#| column: margin

source("common.R")
use_cheatsheet_logo(
  "Peanut", 
  alt = "Hex logo for Peanut - A peanut with a small three node network."
)

sheet_name <- tools::file_path_sans_ext(knitr::current_input())
pdf_preview_link(sheet_name)
translation_list(sheet_name)
```

<!-- Page 1 -->

## Basics

**ggplot2** is based on the **grammar of graphics**, the idea that you can build every graph from the same components: a **data** set, a **coordinate system**, and **geoms**---visual marks that represent data points.

```{r}
library(PNetica)
```

## Warehouses

   - `r args(PnetWarehouse)`
   - `r args(PnodeWarehouse)`
   - `r args(WarehouseManifest)`
   - `r args(is.PnodeWarehouse)`, `r args(is.PnetWarehouse)`,
   - `r args(is.legal.name)`, `r args(as.legal.name)`
   - `r args(is.valid)`
   - `r args(BuildNetManifest)`, `r args(BuildNodeManifest)`
   - `r args(WarehouseData)`
   - `r args(WarehouseFetch)`
   - `r args(WarehouseMake)`
   - `r args(WarehouseSupply)`
   - `r args(WarehouseFree)`, `r args(ClearWarehouse)`
   - `r args(WarehouseCopy)`
   - `r args(WarehouseSave)`
   - `r args(WarehouseUnpack)`

## Network Generic Functions

   - `r args(Pnet)`, `r args(is.Pnet)`, `r args(as.Pnet)`
   - `r args(PnetPnodes)`
   - `r args(PnetOnodes)`
   - `r args(PnetName)`, `r args(PnetTitle)`, `r args(PnetDescription)`
   - `r args(PnetPathname)`
   - `r args(PnetFindNode)`
   - `r args(PnetPriorWeight)`
   
## Node Generic Functions

   - `r args(Pnode)`, `r args(is.Pnode)`, `r args(as.Pnode)`
   - `r args(is.Onode)`
   - `r args(PnodeNet)`
   - `r args(PnodeName)`, `r args(PnodeTitle)`, `r args(PnodeDescription)`
   - `r args(PnodeParents)`,
   - `r args(PnodeParentNames)`, `r args(PnodeNumParents)`, `r args(PnodeParentStates)`
   - `r args(isPnodeContinuous)`
   - `r args(PnodeLabels)`
   - `r args(PnodeStates)`, `r args(PnodeStateTitles)`, `r args(PnodeStateDescriptions)`,
   - `r args(PnodeStateValues)`
   - `r args(PnodeStateBounds)`
   - `r args(PnodeProbs)`
   - `r args(PnodePriorWeight)`, `r args(PnodePostWeight)`, `r args(GetPriorWeight)`
   

## Node Parameterizations

   - `r args(PnodeQ)`
   - `r args(PnodeRules)`
   - `r args(PnodeLink)`
   - `r args(PnodeAlphas)`, `r args(PnodeLnAlphas)`
   - `r args(PnodeBetas)`
   - `r args(PnodeDefaultAlphas)`, `r args(PnodeDefaultBetas)`
   - `r args(PnodeParentTvals)`
   - `r args(PnodeLinkScale)`


## Parameter Calculation

- `r args(BuildAllTables)`, `r args(BuildTable)`
- `r args(GEMfit)`
- `r args(calcPnetLLike)`
- `r args(calcExpTables)`
- `r args(maxCPTParm)`, `r args(maxAllTableParams)`

## Inference and Statistics

- `r args(PnetCompile)`
- `r args(PnetMakeStubNodes)`, `r args(PnetRemoveStubNodes)`
- `r args(PnetDetach)`, `r args(PnetCompile)`
- `r args(PnetEvidence)`
- `r args(Statistics)`
- `r args(StatName)`, `r args(StatNode)`, `r args(StatFun)`
- `r args(PnodeMargin)`, `r args(PnodeEAP)`, `r args(PnodeSD)`, `r args(PnodeMedian)`, `r args(PnodeMode)`
- `r args(calcStat)`, `r args(calcStats)`
- `r args(buildStats)`
- `r args(setNodes)`

<!-- Page 2 -->

## Four Matrix

## Graph Layout

   - `r args(PnodeVisPos)`
   - `r args(pnet2Igraph)`
   - `r args(PnetIGLayout)`

## Gadgets

- `r args(CompensatoryGadget)`, `r args(MakeCompensatoryGadget)`
- `r args(OffsetGadget)`, `r args(MakeOffsetGadget)`
- `r args(RegressionGadget)`, `r args(MakeRegressionGadget)`
- `r args(DPCGadget)`, `r args(MakeDPCGadget)`

## Utilities

- `r args(allCombinations)`
- `r args(buildEMTable)`
- `r args(flog.try)`
- `r args(flattenStats)`



------------------------------------------------------------------------

CC BY SA Russell G. Almond • [ralmond\@fsu.edu](mailto:ralmond@fsu.edu) • [ralmond.net](https://ralmond.net)

Learn more at [https://ralmond.net/Peanut](https://ralmond.net/Peanut).

Updated: `r format(Sys.Date(), "%Y-%m")`.

```{r}
#| output: true

packageVersion("Peanut")
```

------------------------------------------------------------------------
