---
title: "Bayes net manipulation with Peanut :: Cheat Sheet"
description: " "
execute:
  eval: true
  output: false
  warning: false
---

```{r}
#| output: asis
#| echo: false
#| column: margin

source("common.R")
use_cheatsheet_logo(
  "Peanut", 
  alt = "Hex logo for Peanut - A peanut with a small three node network."
)

sheet_name <- tools::file_path_sans_ext(knitr::current_input())
pdf_preview_link(sheet_name)
translation_list(sheet_name)
```

<!-- Page 1 -->

## Basics

**ggplot2** is based on the **grammar of graphics**, the idea that you can build every graph from the same components: a **data** set, a **coordinate system**, and **geoms**---visual marks that represent data points.

```{r}
library(PNetica)
```

## Warehouses

   - `PnetWarehouse`
   - `PnodeWarehouse`
   - `WarehouseManifest`
   - `is.PnodeWarehouse`, `is.PnetWarehouse`,
   - `is.legal.name`, `as.legal.name`
   - `is.valid`
   - `BuildNetManifest`, `BuildNodeManifest`
   - `WarehouseData`
   - `WarehouseFetch`
   - `WarehouseMake`
   - `WarehouseSupply`
   - `WarehouseFree`, `ClearWarehouse`
   - `WarehouseCopy`
   - `WarehouseSave`
   - `WarehouseUnpack`

## Network Generic Functions

   - `Pnet`, `is.Pnet`, `as.Pnet`
   - `PnetPnodes`
   - `PnetOnodes`
   - `PnetName`, `PnetTitle`, `PnetDescription`
   - `PnetPathname`
   - `PnetFindNode`
   - `PnetPriorWeight`
   
## Node Generic Functions

   - `Pnode`, `is.Pnode`, `as.Pnode`
   - `is.Onode`
   - `PnodeNet`
   - `PnodeName`, `PnodeTitle`, `PnodeDescription`
   - `PnodeParents`,
   - `PnodeParentNames`, `PnodeNumParents`, `PnodeParentStates`
   - `isPnodeContinuous`
   - `PnodeLabels`
   - `PnodeStates`, `PnodeStateTitles`, `PnodeStateDescriptions`,
   - `PnodeStateValues`
   - `PnodeStateBounds`
   - `PnodeProbs`
   - `PnodePriorWeight`, `PnodePostWeight`, `GetPriorWeight`
   

## Node Parameterizations

   - `PnodeQ`
   - `PnodeRules`
   - `PnodeLink`
   - `PnodeAlphas`, `PnodeLnAlphas`
   - `PnodeBetas`
   - `PnodeDefaultAlphas`, `PnodeDefaultBetas`
   - `PnodeParentTvals`
   - `PnodeLinkScale`


## Parameter Calculation

- `BuildAllTables`, `BuildTable`
- `GEMfit`
- `calcPnetLLike`
- `calcExpTables`
- `maxCPTParm`, `maxAllTableParams`

## Inference and Statistics

- `PnetCompile`
- `PnetMakeStubNodes`, `PnetRemoveStubNodes`
- `PnetDetach`, `PnetCompile`
- `PnetEvidence`
- `Statistics`
- `StatName`, `StatNode`, `StatFun`
- `PnodeMargin`, `PnodeEAP`, `PnodeSD`, `PnodeMedian`, `PnodeMode`
- `calcStat`, `calcStats`
- `buildStats`
- `setNodes`

<!-- Page 2 -->

## Four Matrix

## Graph Layout

   - `PnodeVisPos`
   - `pnet2Igraph`
   - `PnetIGLayout`

## Gadgets

- `CompensatoryGadget`, `MakeCompensatoryGadget`
- `OffsetGadget`, `MakeOffsetGadget`
- `RegressionGadget`, `MakeRegressionGadget`
- `DPCGadget`, `MakeDPCGadget`

## Utilities

- `allCombinations`
- `buildEMTable`
- `flog.try`
- `flattenStats`



------------------------------------------------------------------------

CC BY SA Russell G. Almond • [ralmond\@fsu.edu](mailto:ralmond@fsu.edu) • [ralmond.net](https://ralmond.net)

Learn more at [https://ralmond.net/Peanut](https://ralmond.net/Peanut).

Updated: `r format(Sys.Date(), "%Y-%m")`.

```{r}
#| output: true

packageVersion("Peanut")
```

------------------------------------------------------------------------
